Fig 2

### 2020-08-21 analysis/boneyard.Rmd
now appropriately names, some DEG anlaysese moved to boneyard

>>>>

# Table 1. Candidate genes and differentially expressed genes

## Genes of interest

```{r candidategenes}
parentalcaregenes <- read_csv("../metadata/03_parentalcaregenes.csv") %>% select(-X1)
candidategenes <- parentalcaregenes %>% pull(gene) 
candidategenes

GOgenes <- parentalcaregenes %>% distinct(GO)  %>% drop_na() %>% pull(GO)
GOgenes

literaturegenes <- parentalcaregenes %>% 
  distinct(literature) %>% 
  drop_na() %>% 
  pull(literature)
literaturegenes

litNotGO <-  literaturegenes[!literaturegenes %in% GOgenes]
litNotGOknown <- litNotGO[!litNotGO %in% c("ADRA2A", "MEST", "SLC6A4")]
litNotGOknown
```

## Differentially expressed genes (DEGs)

```{r}
# summary DEG results from DESeq2
allDEGS <- read_csv("../results/suppltable1.csv") %>%
   mutate(posneg = ifelse(lfc >= 0, "+", "-"),
         sex = recode(sex, "female" = "F", "male" = "M" ),
         tissue = recode(tissue, 
                         "hypothalamus" = "H",
                         "pituitary" = "P", "gonad" = "G"),
         comparison = recode(comparison, 
                         "bldg_lay" = "Bldg2Lay",
                         "lay_inc.d3" = "Lay2Inc3", 
                         "inc.d3_inc.d9" = "Inc3toInc9",
                         "inc.d9_inc.d17" = "Inc9toInc17",
                         "inc.d17_hatch" = "In17toHatch",
                         "hatch_n5" = "Hatch2N5",
                         "n5_n9" = "N5toN9"),
         group = paste(sex, tissue, sep = "")) %>%
  mutate(res = paste("(", posneg, ")", sep = "")) %>%
  mutate(compres = paste(comparison, res, sep = "")) %>%
  select(gene, group, compres) 
allDEGS

DEGsbytissue <- function(whichtissueshorthand, whichsex){

  df <- allDEGS %>%
  filter(grepl(whichtissueshorthand, group),
         grepl(whichsex,group)) %>%
  group_by(group,gene) %>%
  summarize(results = str_c(compres, collapse = "; ")) %>%
  mutate(n = (str_count(results, pattern = ";"))+1) %>%
  arrange(desc(n))  %>%
  filter(n>1)
  #group_by(comparisons) %>%
  #summarize(genes = str_c(gene, collapse = "; "))

  print(head(df))
  return(df)

hmDEGs <- DEGsbytissue("H", "M")
pmDEGs <- DEGsbytissue("P", "M")
gmDEGs <- DEGsbytissue("G", "M")

hfDEGs <- DEGsbytissue("H", "F")
pfDEGs <- DEGsbytissue("P", "F")
gfDEGs <- DEGsbytissue("G", "F")

maleDEGs <- rbind(hmDEGs, pmDEGs) %>%
  rbind(., gmDEGs)
maleDEGs

femaleDEGs <- rbind(hfDEGs, pfDEGs) %>%
  rbind(., gfDEGs)
femaleDEGs

summarizedDEGs <- rbind(femaleDEGs,maleDEGs) %>%
  group_by(group, results) %>%
  summarize(genes = str_c(gene, collapse = "; ")) 
summarizedDEGs

```{r writefiles}
write.csv(summarizedDEGs,"../results/summarizedDEGsv2.csv")

### 2020-08-21 analysis/figure-2-new.Rmd
now appropriately names, some DEG anlaysese moved to boneyard

```{r write}
pdf(file="../figures/fig2-new-1.pdf", width=7, height=7)
plot(fig)
dev.off()

png("../figures/fig2-new-1.png", width = 7, height = 7, 
    units = 'in', res = 300)
plot(fig) 
dev.off()

>>>>

```{r write}
pdf(file="../figures/fig2-1.pdf", width=7, height=7)
plot(fig)
dev.off()

png("../figures/fig2-1.png", width = 7, height = 7, 
    units = 'in', res = 300)
plot(fig) 
dev.off()
